### 2010-06-07 docs/architecture/architecture.tex
more vis

{\tt Amrvis} is a visualization tool developed at LBL for 2- and 3-d
datasets which can plot slices through 3-d datasets as well as
volume-renderings.  It is distributed separately from the MAESTRO
distribution.

@@

VisIt is a powerful, DOE-supported visualization tool for 2- and 3-d
datasets.  It can do contouring, volume rendering, streamlines, ...\
directly from BoxLib plotfiles (to open a plotfile in VisIt, point to
the {\tt Header} file inside the plotfile directory.  Details on
visit can be found at {\tt https://wci.llnl.gov/codes/visit/home.html}\,.

>>>>

{\tt Amrvis} is an easy-to-use visualization tool developed at LBL for
2- and 3-d datasets which can plot slices through 3-d datasets as well
as volume-renderings.  It can also very easily extract 1-d lines
through the dataset along any coordinate direction.  It is distributed
separately from the MAESTRO distribution.

@@

VisIt is a powerful, DOE-supported visualization tool for 2- and 3-d
datasets.  It can do contouring, volume rendering, streamlines, ...\
directly from BoxLib plotfiles (to open a plotfile in VisIt, point to
the {\tt Header} file inside the plotfile directory).  Details on
visit can be found at {\tt https://wci.llnl.gov/codes/visit/home.html}\,.
